An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-11-05 EconGrowth2.Rnw
Now including LINEX parameter tables and candlestick graphs in appendix.

The 95\% confidence intervals associated with Figure~\ref{fig:}
are shown in Table~\ref{tab:} and Figure~\ref{fig:}
**** Ensure that we have figures for all nestings. ****

>>>>

The 95\% confidence intervals associated with Figure~\ref{fig:LINEXq_Resample_Graph}
are shown in Table~\ref{tab:LINEX_Parameters_With_Q} and Figure~\ref{fig:LINEXq_Params_Graph}.
